\documentclass[11pt, a4paper]{report}
\usepackage[utf8]{inputenc} 
\usepackage{fullpage}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}

% Allow display breaks (in \align for example)
\allowdisplaybreaks
\usepackage[hidelinks]{hyperref,xcolor}
\renewcommand\UrlFont{\color{blue}\rmfamily}

% Bibliography management
%  see https://www.overleaf.com/learn/latex/Biblatex_citation_styles
%  and https://www.overleaf.com/learn/latex/Bibliography_management_in_LaTeX
% to use overleaf with reference manager
%  see: https://no.overleaf.com/blog/639-tip-of-the-week-overleaf-and-reference-managers
% \usepackage[backend=biber]{biblatex}
% \addbibresource{library.bib} %Imports bibliography file
 
% Title of your project
\title{Exercises}

% Name of deliverable
\newcommand{\deliverableName}{Practical Work 1}

% Group names(s)
\author{Mark Safrónov}

% Group number
\newcommand{\groupNumber}{MESIIA 2024-2025}

% Any comments for us
\newcommand{\comments}{Comments for teachers of the course}

 % Web address for the project (if any)
\newcommand{\homepage}{\url{https://www.ntnu.edu/studies/courses/IT3010}}

% Date for title page, default is today and 
\date{\today}


\makeatletter{} 

\begin{document}

\input{./title.tex}

\tableofcontents

\section{Introduction}

\input{./unit03ex05.tex}
\input{./unit04ex07.tex}
\input{./unit04ex08.tex}
\input{./unit05ex08.tex}
\input{./unit06ex08.tex}
\input{./unit07ex13.tex}

%\input{./unit07ex08.tex}

%\printbibliography 
\begin{thebibliography}{11}

\bibitem{NTRU8}
EEES\#1: Implementation aspects of NTRUEncrypt, Version 3.1.
2015. Efficient Embedded Security Standards (EESS). 
Available at
\url{https://github.com/NTRUOpenSourceProject/ntru-crypto/blob/master/doc/EESS1-v3.1.pdf}.

\bibitem{IEEENTRU}
IEEEP1363, Standard Specifications For Public-Key Cryptography. 
\url{http://grouper.ieee.org/groups/1363/}.

\bibitem{Merkle}
R. C. Merkle.
A certified digital signature
\emph{Advances in Cryptology -- CRYPTO’ 89}, Lecture Notes in Computer Science, vol 435, pp. 218--238.
	
\bibitem{Knuth}
D. E. Knuth. 
Art of computer programming, volume 2: Seminumerical algorithms. 
Addison-Wesley Professional, 2014.

\bibitem{whatsapp}
WhatsApp Inc.
WhatsApp Encryption Overview. Technical Whitepaper.
Version 8 Updated August 19, 2024
2024.
Available at \url{https://www.whatsapp.com/security/WhatsApp-Security-Whitepaper.pdf}.
Accessed 2024-11-09.
\end{thebibliography}

\end{document}
